Summarize results on robustness of EM algorithm

### 2015-11-05 analysis/investigate_hu_badcoverage.Rmd
small update

```{r}
  eg=load_example(dsc_shrink,42,"flat-top",method="ash.hu.s","../output")
  eg$output$fitted.g
```

@@

Can we find an example?
```{r}
  table((ash.u.s.spiky %>% filter(value==0))$seed)
  eg =load_example(dsc_shrink,seed = 39,method="ash.u.s",scenario="spiky","../output")
```

>>>>

```{r}
  eg=load_example(dsc_shrink,42,"flat-top",method="ash.hu.s","../code/dsc-shrink")
  eg$output$fitted.g
```

@@

Can we find an example?
```{r}
  table((ash.u.s.spiky %>% filter(value==0))$seed)
  eg =load_example(dsc_shrink,seed = 39,method="ash.u.s",scenario="spiky","../code/dsc-shrink")
```

### 2015-11-05 analysis/plot_cdf_eg.Rmd
small update

#df is a list with components method,seed, scenario
#cdf is evaluated at x
#returns list of x,y,pi0, where cdf values are in y
get_cdf = function(df,dsc=dsc_shrink,x=seq(-6,6,length=100),homedir="../output"){
  m=df$method
  if(m=="truth"){m="ash.n"}
  temp=load_example(dsc,df$seed,df$scenario,m,homedir)
  pi0=temp$meta$pi0

>>>>

#df is a list with components method,seed, scenario
#cdf is evaluated at x
#returns list of x,y,pi0, where cdf values are in y
get_cdf = function(df,dsc=dsc_shrink,x=seq(-6,6,length=100),homedir="../code/dsc-shrink"){
  m=df$method
  if(m=="truth"){m="ash.n"}
  temp=load_example(dsc,df$seed,df$scenario,m,homedir)
  pi0=temp$meta$pi0

### 2015-11-05 analysis/summarize_dsc_robust.Rmd
small update

```{r}
  quantile((res %>% filter(method=="ash.n"))$score.diff1,c(0.8,0.9,0.95,0.99,1))
  quantile((res %>% filter(method=="ash.hu"))$score.diff1,c(0.8,0.9,0.95,0.99,1))
  quantile((res %>% filter(method=="ash.u"))$score.diff1,c(0.8,0.9,0.95,0.99,1))

  plot(ecdf((res %>% filter(method %in% c("ash.u","ash.hu")))$score.diff1),ylim=c(0.8,1))
  plot(ecdf((res %>% filter(method %in% c("ash.n")))$score.diff1),ylim=c(0.8,1))
```

```{r}
  mean((res %>% filter(method %in% c("ash.u","ash.hu")))$score.diff1<0.02)
  mean((res %>% filter(method %in% c("ash.u","ash.hu")))$score.diff1>1)
  mean((res %>% filter(method %in% c("ash.n")))$score.diff1<0.02)  
```

Now check out the example that showed the biggest convergence problem
```{r}
#check out which one showed biggest convergence problem
prob = res[which.max(res$score.diff1),]
prob_eg = load_example(dsc_robust,seed=prob$seed,scenario=as.character(prob$scenario),method=as.character(prob$method),homedir="../output")
```

>>>>

```{r}
  quantile((res %>% filter(method=="ash.n"))$diff1,c(0.8,0.9,0.95,0.99,1))
  quantile((res %>% filter(method=="ash.hu"))$diff1,c(0.8,0.9,0.95,0.99,1))
  quantile((res %>% filter(method=="ash.u"))$diff1,c(0.8,0.9,0.95,0.99,1))

  plot(ecdf((res %>% filter(method %in% c("ash.u","ash.hu")))$diff1),ylim=c(0.8,1))
  plot(ecdf((res %>% filter(method %in% c("ash.n")))$diff1),ylim=c(0.8,1))
```

```{r}
  mean((res %>% filter(method %in% c("ash.u","ash.hu")))$diff1<0.02)
  mean((res %>% filter(method %in% c("ash.u","ash.hu")))$diff1>1)
  mean((res %>% filter(method %in% c("ash.n")))$diff1<0.02)  
```

Now check out the example that showed the biggest convergence problem
```{r}
#check out which one showed biggest convergence problem
prob = res[which.max(res$diff1),]
prob_eg = load_example(dsc_robust,seed=prob$seed,scenario=as.character(prob$scenario),method=as.character(prob$method),homedir="../code/dsc-robust")
```
